%
% Sample introduction of your thesis
%

\chapter{Introduction}
Physical access to otherwise secure systems has become much more common due to the widespread use of embedded devices in today's world. This circumstance enables attacks that are impossible in more restricted scenarios and thus, the need for countermeasures against such physical attacks. 

Indeed, glitching a system, i.e., introducing a physical disturbance such that the execution of the processor is influenced, is one of the many ways attackers may be able to leverage this increased level of access. These hardware-induced faults have already been used to compromise commercially available systems, most notably the XBOX 360\,\cite{free60} and PlayStation 3\,\cite{ps3hyper}. Similar to Side-Channel Analysis\,\cite{standaert2010introduction}, glitching-based attacks offer a new angle of attack against systems that are running semantically secure software without any conventional vulnerabilities.

Although fault attacks against cryptographic computations have been studied extensively in the past\,\cite{boneh1997importance}\todo{cite more}, precise glitching enables much more devious attacks, such as gaining \texttt{root} access by flipping only a single bit in the \texttt{sudo} binary\,\cite{gruss2018another}. Instead of merely faulting the computation of an important value, glitches are used to alter the executed instructions, e.g., altering the condition on a branch instruction, and hence violate the control flow integrity of the attacked program.  As a result of this, many of the suggested defences against fault attacks, e.g., redundant computations\cite{chang2019evaluating}, can be skipped or circumvented entirely. After all, why forge a signature when you can simply skip the signature check?\todo{too informal}

In this paper we introduce a formal description of hardware-induced faults and give an overview of \todo{Von anderen Papern vorgeschlagen??} defences suggested by related works. We categorise these countermeasures by whether they are software-only, hardware-only or require a hybrid solution and evaluate them within those categories, based on their quality (error detection rate and latency) and their induced overhead in memory or runtime.

\todo[inline]{Short overview of attack categories (control flow violation vs. faulty computation)}
\todo[inline]{Short overview of defence categories (control flow integrity via signatures; redundant computations)}